### 2021-03-08 README.Rmd
small update to readme

The directory containing these files can be found on any system where skater is installed:

```{r}
system.file("extdata", "sampleids-1000g-unrelated", package="skater", mustWork=TRUE)
```

>>>>

The directory containing these files can be found on any system where skater is installed. On MacOS, this is usually something like `/Library/Frameworks/R.framework/Versions/4.0/Resources/library/skater/extdata/sampleids-1000g-unrelated`.

```{r, eval=FALSE}
system.file("extdata", "sampleids-1000g-unrelated", package="skater", mustWork=TRUE)
```
